---
title: "CovidPlots"
output: 
    github_document:
        toc: true
        toc_depth: 4
date: '`r format(Sys.time(), "%d %B %Y %I:%M %p %Z")`'
---


```{r, setup, include=FALSE}
knitr::opts_chunk$set(out.width = 4800,  fig.width = 12, fig.asp=0.62,  dev = 'svg') 
knitr::opts_chunk$set(echo = TRUE)
```

```{r, county_setup, include=FALSE}
    source("nytimes_us_counties.r")
    subtext = "Data from NY Times via covid-19.datasettes.com"

```

## Covid by County  
### Selected Counties


Covid case counts and death counts by county, based on daily data from NY Times via https://covid-19.datasettes.com  

```{r, plot_counties, echo=FALSE, results='hide', message=FALSE,warning=FALSE}
first_day <- ISOdate(2020,3,1, tz="")
links <- CreateCountyPlots(countyPopulations, first_day)

```

### County Details

```{r, plot_counties_links, echo=FALSE, results='asis', message=FALSE,warning=FALSE}
   for (l in links){
      cat (l, "\n")
   }
```
 
## CDC All Deaths by Week
 The CDC Flu View website gives weekly deaths by state going back several years. Data entry and reporting lags by many weeks, so the last month or so of deaths will be under-reported or missing.
 
 https://gis.cdc.gov/grasp/fluview/mortality.html
 
 ```{r, cdc_all_deaths, echo=FALSE, results='hide', message=FALSE,warning=FALSE}
   source("cdc_deaths.r")
   print(p_all_deaths_recent)
   print(p_year_on_year_linear)
   print(p_year_on_year)
 
 ```
 
 
 
 
 
## Covid in US States
 Covid positive tests, deaths, and hospitalizations by state from covidtracking.com https://covidtracking.com

### Hospitalizations

 ```{r,  state_hospital, echo=FALSE, results='hide', message=FALSE,warning=FALSE}
     source("covidtracking_us_states.r")
   print (p_hosp)
   print(p_hospPer)
 ```

### Tests

 ```{r,  state_positves, echo=FALSE, results='hide', message=FALSE,warning=FALSE}

   print(p_positives)
   print(p_positive_fraction)
   print(p_positivesPer)
   print (p_deltaPositivesPer)
   print(p_total_tests)
   print(p_total_tests_per)
 ```

### Deaths

 ```{r,  state_deaths, echo=FALSE, results='hide', message=FALSE,warning=FALSE}

   print(p_deaths_liner)
   print(p_deaths)
   print(p_deltaDeaths)
   print(p_deathsPerLinear)
   print (p_deathsPer)
   print(p_deltaDeathsPer)

 ```


## Covid in China

 Covid data from Johns Hopkins CSSE via https://covid-19.datasettes.com
 ```{r,  china, echo=FALSE, results='hide', message=FALSE,warning=FALSE}
     source("covid_international.r")
     print(p_china)
     print(p_china_deaths)
 ```

## Covid in Scandanavia
 ```{r,  scandanavia, echo=FALSE, results='hide', message=FALSE,warning=FALSE}
   print(p_scandanavia)
   print(p_scandanavia_per)
   print(p_scandanavia_per_log2)
   print(p_scandanavia_deaths)
   print(p_scandanavia_deaths_per_linear)
   print(p_scandanavia_deaths_per_slope)
   print(p_scandanavia_deaths_per)
   print(p_scandanavia_deaths_per_log2)
```